---
title: "hw6"
author: "Yuqi Miao"
date: "11/16/2019"
output: github_document
---

```{r include=FALSE}
library(tidyverse)
library(broom)
library(readxl)
library(viridis)
library(modelr)

knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE)

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis")

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

theme_set(theme_minimal() + theme(legend.position = "bottom"))
```

# Problem 1

## data cleaning

```{r}
birthweight <- read_csv(file = "data/birthweight.csv") %>% 
    janitor::clean_names() %>% 
    mutate(
        babysex = factor(babysex,levels = c(1,2), labels =c("male","female")),
        frace = factor(frace, levels = c(1,2,3,4,8,9),labels = c("White","Black","Asian","Puerto Rican","Others","Unknown")),
        malform = factor(malform, levels = c(0,1), labels = c("absent","present")),
        mrace = factor(mrace, levels = c(1,2,3,4,8,9),labels = c("White","Black","Asian","Puerto Rican","Others","Unknown"))
    )
```

## building data driven model

### Doing SLR by making plots?

```{r}
# birthweight %>%
#     select_if(is.numeric) %>% ## Only select continuous var
#     select(-pnumlbw,-pnumsga,-parity) %>% ## rule out 2 columns with only # 0:pnumlbw,pnumsga,parity
#     mutate_if(is.numeric, list(scale)) %>% ## scale the variables
#     pivot_longer(cols = -bwt, names_to = "factor",values_to = "value") %>% 
#     ggplot(aes(x = value, y = bwt,color = factor)) + 
#     geom_point(alpha = 0.5, size = 0.5)+
#     geom_smooth(method = "lm",lwd = 0.2) +
#     scale_x_continuous(limits = c(0,2))+
#     facet_grid(.~factor)
 ## Because the predictors and outcome have different scales, firstly, I use scale to make every variable in (0,1), then filter the ones with only (or mostly 0),which is `pnumlbw`,`pnumsga`,`parity`,According to the simple linear regreassion results shown in the plot, choosing `bhead`,`blength`,`delwt`,`mheight`,`wtgain` as my model predictor.
### making a overal mlr
```

### overall regression among all variables.
```{r}
mlr_all=lm(bwt~.,data = birthweight)
summary(mlr_all)
```
Based on the overall regression, choosing the significant predictors to build a model, which includes `babysex`,`bhead`,`blength`,`delwt`,`gaweeks`,`mrace`,`smoke`.

  

### model building

```{r}
mlr_1 <- birthweight %>% 
    mutate(
        mrace = fct_infreq(mrace),
        babysex = fct_infreq(babysex)
        ) %>% 
    lm(bwt~babysex+bhead+blength+delwt+mrace+gaweeks+smoken,data = .)
summary(mlr_1)

```
### add the fitted value and residuals
```{r}
birthweight %>% 
    modelr::add_residuals(mlr_1) %>% 
    modelr::add_predictions(mlr_1) %>% 
    ggplot(aes(y = resid, x = pred)) +
    geom_point(color = "darkblue", alpha = 0.5,size = 0.5)+
    geom_smooth(method = "lm")
```

As shown in plot, the residual and fitted value has no clear linear relationship.

## Comparing models

```{r}
mlr_2 <- lm(bwt~blength+ gaweeks,data = birthweight)
mlr_3 <- lm(bwt~bhead*blength*babysex, data = birthweight)
summary(mlr_3)
```


### Cross validation comparision
```{r}
cv_bwt <- 
    crossv_mc(birthweight,100) %>% 
    mutate(
        train = map(train, as.tibble),
        test = map(test,as.tibble)
    ) 
cv_bwt = cv_bwt %>% 
    mutate(
        model1 = map(train,~lm(bwt~babysex+bhead+blength+delwt+mrace+gaweeks+smoken,data = .x)),
        model2 = map(train,~lm(bwt~blength+ gaweeks,data = .x)),
        model3 = map(train,~lm(bwt~bhead*blength*babysex, data = .x))
    ) %>% 
    mutate(
        rmse_model1=map2_dbl(model1, test,~rmse(model = .x,data = .y)),
        rmse_model2=map2_dbl(model2, test,~rmse(model = .x,data = .y)),
        rmse_model3=map2_dbl(model3, test,~rmse(model = .x,data = .y))
    )
cv_bwt %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "models",
    values_to = "rmse",
    names_prefix = "rmse_"
  ) %>% 
  mutate(
    names = fct_inorder(ordered = rmse,f = models )
  ) %>% 
  ggplot(aes(x = models, y = rmse))+
  geom_violin()
  
    
```


  
```




















